---
title: "Lab4"
author: "Rae Fuhrman"
date: "1/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(Ecdat)
library(plm)
library(lmtest)
library(car)

```

Part 1. Non linear least squares (logistic growth of bacteria)

```{r}

CellGrowth <- read_csv("CellGrowth.csv")

ggplot(CellGrowth, aes(x=Time, y=CellCount))+
  geom_point()

#find estimates for logistic growth
#N = A/(1+Be^(-rt))
#OK, now if N0 is 2000 (from graph), what is B?

Bestimate <- (3700-2000/2000) #B=~.85

#now let's estimate r the growth rate

lag_phase <- CellGrowth %>% 
  filter(Time < 5)

#relationship between natural log and time should be linear
ggplot(lag_phase, aes(x=Time, y=log(CellCount)))+
  geom_point()
#looks pretty linear which means yes it was probably close to an exponential relationship

lm(log(CellCount) ~ Time, data = lag_phase) #r=0.1035 

```

Find model A, B, and r using Gauss-Newton method for iterative convergence (nonlinear least squares):

Use the nls() function:

```{r}

cell_fit <- nls(CellCount ~ A/(1+B*exp(-r*Time)),
                start = list(A = 3700, B = 0.85, r = 0.1035),
                data = CellGrowth,
                trace = TRUE) #exp() is e raised to something, trace = true gives all convergence values

cell_fit

A <- coef(cell_fit)[1]  # will automatically update if model is updates 
B <- coef(cell_fit)[2]
r <- coef(cell_fit)[3]

#create a new sequence of time values (time_seq)
time_seq <- seq(0,20,length = 100)

#plug that new sequence into my model with the paramters A,B,r 
cell_pred <- A/(1+B*exp(-r*time_seq))

#bind that together with the time sequence data using data.frame to create a predicted data frame
pred_df <- data.frame(time_seq, cell_pred) #combine for plotting

ggplot(CellGrowth, aes(x = Time, y = CellCount)) + 
  geom_point(colour = "blue", size = 3) + 
  theme_bw() +
  geom_line(data = pred_df, aes(x = time_seq, y = cell_pred), colour = "orange", size = 1) + 
  xlab("Time (h)") +
  ylab("Cell Count") +
  ggtitle("Bacterial Growth")

```

Panel Regression - First Shot

State: our entity variable
Year: our time variable
packpc: our DV
avgprs: our predictor variable


```{r}

cigs_panel <- Cigarette %>% 
  select(state, year, packpc, avgprs)

ggplot(cigs_panel, aes(x=avgprs, y=packpc, group=state))+
  geom_point(aes(color=state))+
  geom_smooth(method="lm", aes(color=state), se=FALSE, size=0.2)

ggplot(cigs_panel, aes(x=year, y=packpc, group = state))+
  geom_point(aes(color=state))+
  geom_smooth(method="lm", aes(color=state), size=0.3, se=FALSE)

```

Entity fixed effects model:

```{r}

cigs_model <- plm(packpc ~ avgprs,
                  data=cigs_panel,
                  index = c("state", "year"),
                  model = "within")
cigs_model

coeftest(cigs_model, vcov.=vcovHC(cigs_model, type = "HC1"))

```
```{r}

et_cigs_model <- plm(packpc ~ avgprs,
                data = cigs_panel,
                index = c("state","year"),
                model = "within",
                effect = "twoways")

et_cigs_model

coeftest(et_cigs_model, vcov. = vcovHC(et_cigs_model, type = "HC1")) #coefficient is still highly significant, but is a different value

pFtest(et_cigs_model,cigs_model) #must give more complete model first, time complete in this case

```

**Conclusion:** Yes, we should include time fixed effects.  This makes sense, because we know that cigarette use is decreasing universally over time due to so many factors - health, societal pressure, etc.  We would expect time to substantially influence the number of packs per person.

